%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc} % For loading fonts
\usepackage{hyperref}
\usepackage{bibentry}
\hypersetup{
     colorlinks   = true,
     urlcolor    = blue
}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[T1]{fontenc}
%\bibliographystyle{chicago}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Lucy Hackett} % Your name

\begin{document}
\nobibliography{published}
 %
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{}
University of California, Berkeley \hfill Email:  \href{mailto:lucy\_hackett@berkeley.edu}{lucy\_hackett@berkeley.edu}\\
Department of Agricultural and Resource Economics \\
\end{rSection}


\begin{rSection}{Education}

{\bf Ph.D in Agricultural and Resource Economics (in progress)} \hfill {\em August 2020 - Present} 
\\ UC Berkeley\hfill \\
\textit{GPA: 4.0}
\vspace{0.1cm}

{\bf CIDE (Centro de Investigación y Docencia Económicas)} \hfill {\em June 2018} 
\\ Masters in Economics\hfill\\
\textit{Ranked 1\textsuperscript{st} in class}
%Advisor: Fernanda Marquez-Padilla  \\
\vspace{0.1cm}

{\bf University of Oregon, Clark Honors College} \hfill {\em June 2015} 
\\ B.S., Economics and Spanish Literature  \hfill
\\ Minor in Mathematics \hfill 
\\ 
\textit{Summa cum laude}
%Advisor: Glenn Waddell  \\

% \vspace{0.1cm}

% {\bf UNAM} \hfill {\em Fall 2014} 
% \\ Student exchange 
% \\ Mexico City, Mexico 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research and Technical Experience}

\begin{rSubsection}{UC Berkeley}{\textit{2022}}{Research Assistant}{Berkeley, CA}
    \item Ethan Ligon
    \item Ellen Bruno
\end{rSubsection}

\begin{rSubsection}{LNPP (National Lab for Public Policy)}{\textit{ 2018 - 2020}}{Research Assistant}{Mexico City}
\item Supervisor: Dr. Florian Wendelspiess Chávez Juárez
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Economics Department: CIDE}{\textit{ 2018 -  2020}}{Research Assistant}{Mexico City}
\item Supervisors: Dr. Fernanda Marquez Padilla, Dr. Luz Marina Arias 
\end{rSubsection}

\begin{rSubsection}{Economics Department: Univ. of Oregon}{\textit{2014}}{Research Assistant}{Eugene, OR}
\item Supervisor: Dr. Benjamin Hansen
\end{rSubsection}
\end{rSection}


% ------ TEACHING
\begin{rSection}{Teaching experience}

\begin{rSubsection}{UC Berkeley, ARE}{\textit{August 2020 - Present}}{\textbf{Grad. Student Instructor}}{}
\item ARE 212: Econometrics (Spring 2021, 2022)
\item ECON C151: Development (Fall 2021)
\end{rSubsection}

\begin{rSubsection}{Economics Department: CIDE}{\textit{ 2018 -  2020}}{\textbf{Lecturer}}{Mexico City}
\item Macroeconomics (Master's)
\item Macroeconomics (advanced undergraduate)
\end{rSubsection}

\begin{rSubsection}{Economics Department: CIDE}{\textit{ 2017 - 2019}}{\textbf{Teaching Assistant}}{Mexico City}
\item Advanced Macroeconomics (Master's level) 
\item Econometrics II (Master's level).
\end{rSubsection}

\end{rSection}

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards} \itemsep -2pt
\item Award for Best Applied Thesis (CIDE)
\item Presidential Award for Original Research, undergraduate
\item Phi Beta Kappa
\item Oregon Six (identified as one of the 6 most promising students of the U. of Oregon class of 2015)

\end{rSection}

\begin{rSection}{Grants} \itemsep -2pt
\item Tinker Field Research Grant, 2022
\item ARE Student Travel Grant, 2022

\end{rSection}

\begin{rSection}{Publications}
\item Guerrero, Omar, and G. Castañeda, G. Trujillo, L. Hackett and F. Chávez-Juárez. ``Subnational sustainable development: The role of vertical intergovernmental transfers in reaching multidimensional goals''. \textit{Socioeconomic Planning Sciences}, 2021.
\end{rSection}


\begin{rSection}{Presentations}

\begin{rSubsection}{iHEA Annual Conference}{July 2019}{Presented working paper}{Basel, Switzerland}
\item Presented the working paper \textit{The health-care system seen as a complex system: An agent--based approach}, co--authored with Florian Chávez--Juárez, Alejandro Blasco y Georgina Trujillo at the International Health Economics Association (iHEA) Conference.
\end{rSubsection}

\begin{rSubsection}{LACEA Health Workshop}{Nov. 2018}{Presented working paper}{Bogota, Colombia}
\item Presented the working paper \textit{Working for Change: The effect of female labor force participation on fertility}, co--authored with Fernanda Márquez--Padilla at the Latin American and Caribbean Economic Association Health Workshop.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l  @{\hspace{6ex}} @{} >{\bfseries}l @{\hspace{6ex}} l }
Advanced        & Python, Java, Stata, \LaTeX, Git &  \\
Intermediate    & R, Javascript, PHP, SQL &\\
\end{tabular}

\end{rSection}

\begin{rSection}{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l  @{\hspace{6ex}} }
English & Native \\ 
Spanish & Fluent 
%\\ Mexican Sign Language & Basic
\end{tabular}

\end{rSection}

\end{document}
