\documentclass[10pt, a4paper]{letter}

% moderncv options
\moderncvstyle{casual} % or 'banking', 'classic', 'oldstyle'
\moderncvcolor{blue}   % or 'blue', 'orange', 'green', 'red'

% Adjust margins for a more modern, single-page look
\usepackage[scale=0.8]{geometry}

% Personal details
\name{Lucy}{Hackett}
\title{Economist}
\address{Giannini 207, UC Berkeley}
\phone{+1 (510) 326-3451}
\email{lucy\_hackett@berkeley.edu}
\homepage{https://lghackett.github.io}
% Assuming you would add a LinkedIn for the private sector
%\social[linkedin]{[Your LinkedIn Profile]}
%\social[github]{lghackett} % Using your GitHub handle

% Custom commands for visual consistency
\newcommand{\projectrole}[1]{\textbf{\small #1}}
\newcommand{\projectimpact}[1]{\textit{\small #1}}

\begin{document}

% Custom command for sub-bullets
\setlist[itemize, 2]{label=\textendash}

\makecvtitle

% --- PROFESSIONAL SUMMARY ---
\section{Professional Summary}
Highly analytical and results-driven PhD Candidate in \textbf{Agricultural and Resource Economics} with a strong foundation in econometric modeling, spatial analysis, and advanced statistical methods. Seeking to leverage expertise in \textbf{causal inference}, \textbf{big data analysis}, and \textbf{economic modeling} to solve complex business problems in data science, tech, or consulting. Proven ability to translate complex research into actionable insights, communicate findings to diverse audiences, and manage multiple high-impact projects. 

% --- CORE COMPETENCIES ---
\section{Core Competencies}
\begin{itemize}
    \item \textbf{Econometrics \& Statistical Modeling:} Causal Inference (DiD, RDD, IV), Spatial Econometrics, Time-Series, Machine Learning Fundamentals.
    \item \textbf{Data Analysis \& Programming:} Expert in \textbf{Stata, R, and Python} (Pandas, NumPy, Scikit-learn, GeoPandas). Proficient in \textbf{LaTeX}.
    \item \textbf{Data Visualization \& GIS:} Experience with Geographic Information Systems (GIS) and generating clear, professional data visualizations.
    \item \textbf{Domain Expertise:} Environmental Economics, Urban/Spatial Economics, Policy Evaluation, Market Analysis, Policy Evaluation.
\end{itemize}

% --- SELECTED PROJECTS & RESEARCH (Showcasing Impact) ---
\section{Selected Projects \& Research}
\subsection{Quantifying Environmental Risk \& Market Inefficiency in Urban Housing}
\cvlistitem{\projectrole{Role:} Designed an \textbf{equilibrium housing market model} to quantify the economic costs and market response to environmental hazards (land subsidence) in Mexico City}
\cvlistitem{\projectrole{Methodology:} Exploited quasi-random variation in sinking intensity using \textbf{spatial econometric methods} to estimate the impact on property values.}
\cvlistitem{\projectrole{Key Results:} Found that subsidence imposes an estimated \textbf{\$33 billion USD} in economic costs, with \textbf{12\%} due to information frictions that inefficiently increase housing stock in risky areas.}
\cvlistitem{\projectrole{Impact:} Provided evidence on the financial externality of groundwater depletion and the need for improved public information to enhance market efficiency.}

\subsection{Systematic Evaluation of Gains from Water Trading Models}
\cvlistitem{\projectrole{Objective:} Conducted a \textbf{systematic meta-analysis} of peer-reviewed literature to evaluate the accuracy and policy relevance of water trading models.}
\cvlistitem{\projectrole{Methodology:} Developed a framework to assess how models incorporate key local context factors (e.g., third-party impacts, transaction costs, legal environment).}
\cvlistitem{\projectrole{Finding:} Estimates \textbf{vary widely} and are often less likely to account for critical real-world features like transaction costs, impacting policy interpretation.}

\subsection{Modeling Structural Vulnerability to Environmental Hazards}
\cvlistitem{\projectrole{Methodology:} Combined novel \textbf{plot-specific differential subsidence estimates} with a representative resident survey to estimate \textbf{structural fragility curves} and damage thresholds[cite: 109].}
\cvlistitem{\projectrole{Impact:} Extrapolated findings to a city-wide analysis to calculate damages and vulnerability at a city-block level, providing a tool for \textbf{city planning and risk assessment}[cite: 109].}

% --- RESEARCH & PROFESSIONAL EXPERIENCE ---
\section{Research \& Professional Experience}
\cvlistitem{\textbf{Graduate Student Researcher}, UC Berkeley (Various PIs) \hfill 2021–2025 [cite: 108]}
\begin{itemize}
    \item Conducted advanced quantitative research, including model development and data analysis for multiple faculty across departments[cite: 108].
    \item Managed large, complex datasets for projects in environmental, urban, and development economics[cite: 108].
\end{itemize}

\cvlistitem{\textbf{Analyst}, National Laboratory for Public Policy (LNPP) \hfill 2018–2020 [cite: 108]}
\begin{itemize}
    \item Applied economic principles and quantitative methods to evaluate public policy outcomes[cite: 108].
\end{itemize}

% --- EDUCATION ---
\section{Education}
\cventry{Expected May 2026}{PhD, Agricultural and Resource Economics}{University of California, Berkeley}{Berkeley, CA}{}{Dissertation: "Essays in Environmental and Urban Economics" [cite: 14, 15]}
\cventry{2018}{Master's Degree in Economics}{CIDE}{Mexico City, Mexico}{}{Best applied thesis, Class of 2018 [cite: 41, 95]}
\cventry{}{B.Sc. in Economics and Spanish Literature}{University of Oregon}{Eugene, OR}{}{Honors: Phi Beta Kappa [cite: 38, 96]}

% --- GRANTS, FELLOWSHIPS \& AWARDS (Demonstrating Competitiveness) ---
\section{Select Grants \& Awards}
\cvlistitem{\textbf{UC Dissertation Fellowship} (\$37,000) [cite: 87]}
\cvlistitem{\textbf{Fisher Center for Real Estate Research Grant} (\$15,000, awarded twice) [cite: 90, 91]}
\cvlistitem{\textbf{Giannini Foundation Minigrant} (\$35,000) [cite: 91]}
\cvlistitem{CEGA Development Economics Challenge Grant (\$5,000) [cite: 88]}
\cvlistitem{Outstanding Graduate Student Instructor Award [cite: 94]}

% --- TEACHING & MENTORING (For Communication/Leadership Skills) ---
\section{Teaching \& Mentoring Leadership}
\cvlistitem{\textbf{Instructor, Training for New Graduate Student Instructors}, UC Berkeley:} Focused on developing pedagogy and classroom management skills.
\cvlistitem{\textbf{Teaching Fellow, Graduate Econometrics}, UC Berkeley:} Led instructional sections focused on applied regression and statistical modeling.
\cvlistitem{\textbf{Berkeley Economists for Equity (BEE) Mentor}}
\end{document}